Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-01 paper.tex
Discuss BCs
Add figure placeholder for 2-D blade mesh closeup

The computational domain is a rectangular volume 3.66 m long, 3.66 m wide, and
2.44 m tall (for 3-D), with the turbine located 1.52 m from the inlet, and
centered vertically with a vertical axis. with a cylindrical sliding mesh
interface, where the turbine zone rotates at a mean tip speed ratio
$\lambda=1.9$ with a sinusoidal oscillation at the blade passage
frequency---with and amplitude of 0.19 and the first peak at 0.7 radians---to
mimic the experimental data. The 2-D mesh is shown in Figure~\ref{fig:mesh}.

@@

\begin{figure}[ht]
\caption{Snapshot of the 2-D computational mesh.}
\label{fig:mesh}
\end{figure}

@@

Initial and boundary conditions were set to match those of the tow tank as well
as possible.

>>>>

The computational domain is a rectangular volume 3.66 m long, 3.66 m wide, and
2.44 m tall (for 3-D), with the turbine located 1.52 m from the inlet, and
centered vertically with a vertical axis. with a cylindrical sliding mesh
interface, where the turbine zone rotates at a mean tip speed ratio
$\lambda=1.9$ with a sinusoidal oscillation at the blade passage
frequency---with and amplitude of 0.19 and the first peak at 0.7 radians---to
mimic the experimental data. The 2-D mesh overview is shown in
Figure~\ref{fig:mesh} and the blade mesh is shown in
Figure~\ref{fig:blade-mesh}.

@@

\begin{figure}[ht]
    \caption{Overview of the 2-D computational mesh.}

    \label{fig:mesh}
\end{figure}

\begin{figure}[ht]
    \caption{Detailed view of the 2-D computational mesh near the blades.}

    \label{fig:blade-mesh}
\end{figure}

@@

Initial and boundary conditions were set to match those of the tow tank as well
as possible. The velocity at the bottom and side walls was fixed to 1 m/s to
match the tow tank case, while the top boundary condition was a slip velocity
condition. Note that in 2-D the top and bottom boundary conditions are
``empty,'' which is an OpenFOAM convention.
